Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-04-09 article_bihom_v2.tex
typo

		\begin{proposition}[Proposition 3.2.5 in \cite{Bardet04}]
			let $f_1,\dots,f_m$ a semi-regular homogeneous sequence, $f_i$ is of degree $d_i$. Then the following proprieties are verified:
			\begin{itemize}
				\item The sequence $f_1,\dots,f_m$ is semi-regular if and only if it's Hilbert's series is
				$$
					 \prod_{i=1}^{m}(1-z^d_i)/(1-z)^n,
				$$
				The series $S_{m, n}(z) = \sum_{d \geq 0}h_{d, m}(n)z^d = \prod_{i=1}^{m}(1-z^d_i)/(1-z)^n$ is called the generating series of $f_1,\dots,f_m$.
				\item The sequence $f_1,\dots,f_m$ is semi-regular on $\mathbb{F}_2$, if and only if it's Hilbert series is
				$$
				(1-z)^n/\prod_{i=1}^{m}(1+z^d_i),
				$$
				the series $S_{m, n}(z) = \sum_{d \geq 0}h_{d, m}(n)z^d = (1-z)^n/\prod_{i=1}^{m}(1+z^d_i)$ is called the generating series of $f_1,\dots,f_m$.
				\item Every permutation $f_{\sigma(1)},\dots,f_{\sigma(m)}$ est a semi-regular sequence.
				\item When the associated variety is zero-dimensional, $H(I)$ is characterized by
				$$
					\forall d < H(I), h_{d, m}(n) > 0 \text{ and } h_{H(I), m}(n) \leq 0.
				$$
				\item The sequence $f_1,\dots,f_m$ is semi-regular $\nRightarrow \forall i \in [1;m]$, the sequence $f_1,\dots,f_i$ is semi-regular. 
			\end{itemize}
		\end{proposition}

>>>>

		\begin{proposition}[Proposition 3.2.5 in \cite{Bardet04}]
			let $f_1,\dots,f_m$ a semi-regular homogeneous sequence, $f_i$ is of degree $d_i$. Then the following proprieties are verified:
			\begin{itemize}
				\item The sequence $f_1,\dots,f_m$ is semi-regular if and only if it's Hilbert's series is the series $S_{m, n}(z) = \sum_{d \geq 0}h_{d, m}(n)z^d = \prod_{i=1}^{m}(1-z^d_i)/(1-z)^n$ is called the generating series of $f_1,\dots,f_m$.
				\item The sequence $f_1,\dots,f_m$ is semi-regular on $\mathbb{F}_2$, if and only if it's Hilbert series is the series $S_{m, n}(z) = \sum_{d \geq 0}h_{d, m}(n)z^d = (1+z)^n/\prod_{i=1}^{m}(1+z^d_i)$ is called the generating series of $f_1,\dots,f_m$.
				\item Every permutation $f_{\sigma(1)},\dots,f_{\sigma(m)}$ is a semi-regular sequence.
				\item When the associated variety is zero-dimensional, $H(I)$ is characterized by
				$$
					\forall d < H(I), h_{d, m}(n) > 0 \text{ and } h_{H(I), m}(n) \leq 0.
				$$
				\item The sequence $f_1,\dots,f_m$ is semi-regular $\nRightarrow \forall i \in [1;m]$, the sequence $f_1,\dots,f_i$ is semi-regular. 
			\end{itemize}
		\end{proposition}
